Guarded Recursion in Agda via Sized Types

### 2019-01-14 code-oneclock-paper/latex/paper.tex
WIP deep embedding
worked on dfix and force
Added example of streams to tex file
rephrasing deep emb
more work on deep emb
Added keywords and classification

\ccsdesc[100]{General and reference~General literature}
\ccsdesc[100]{General and reference}%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{Dummy keyword}%TODO mandatory; please add comma-separated list of keywords

@@

\newunicodechar{⊤}{$\top$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{₁}{$_1$}
\newunicodechar{₂}{$_2$}
\newunicodechar{₃}{$_3$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{β}{$\beta$}
\newunicodechar{γ}{$\gamma$}
\newunicodechar{ε}{$\varepsilon$}
\newunicodechar{θ}{$\theta$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{κ}{$\kappa$}
\newunicodechar{π}{$\pi$}
\newunicodechar{∈}{$\in$}
\newunicodechar{⊞}{$\boxplus$}
\newunicodechar{⊠}{$\boxtimes$}
\newunicodechar{∁}{$\mathbb{C}$}
\newunicodechar{►}{$\blacktriangleright$}
\newunicodechar{▻}{$\vartriangleright$}
\newunicodechar{𝟙}{\textbf{1}}
\newunicodechar{∙}{$\cdot$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ℓ}{$\ell$}
\newunicodechar{∅}{$\varnothing$}
\newunicodechar{⟶}{$\rightarrow$}
\newunicodechar{□}{$\square$}
\newunicodechar{⇡}{$\uparrow$}
\newunicodechar{⊛}{$\circledast$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{⟨}{$\langle$}
\newunicodechar{⟩}{$\rangle$}
\newunicodechar{■}{$\blacksquare$}
\newunicodechar{∎}{$\blacksquare$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{⊕}{$\oplus$}
\newunicodechar{⊗}{$\otimes$}
\newunicodechar{∼}{$\sim$}
\newunicodechar{≈}{$\approx$}
\newunicodechar{⊔}{$\sqcup$}
\newunicodechar{⟦}{$\llbracket$}
\newunicodechar{⟧}{$\rrbracket$}
\newunicodechar{⊥}{$\bot$}
\newunicodechar{∞}{$\infty$}
\newunicodechar{⇑}{$\Uparrow$}
% Add more as you need them (shouldn't happen often).

@@

@@

\section{Deep Embedding}
\label{sec:syntax}
\input{Prelude/Syntax}

@@

\subsection{Clock Quantification}
\input{CloTT/TypeFormers/WeakenClock}
\input{CloTT/TypeFormers/ClockQuantification}

\subsection{Later}
\input{CloTT/TypeFormers/Later}
\input{CloTT/TypeFormers/Fix}
\input{CloTT/TypeFormers/Force}

>>>>

\ccsdesc[100]{Theory of Computation~Type Theory}
\ccsdesc[100]{Theory of Computation~Categorical Semantics}%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{guarded recursion, type theory, semantics, coinduction, sized types}%TODO mandatory; please add comma-separated list of keywords

@@

\newunicodechar{⊤}{$\top$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{₁}{$_1$}
\newunicodechar{₂}{$_2$}
\newunicodechar{₃}{$_3$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{β}{$\beta$}
\newunicodechar{η}{$\eta$}
\newunicodechar{γ}{$\gamma$}
\newunicodechar{ε}{$\varepsilon$}
\newunicodechar{θ}{$\theta$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{κ}{$\kappa$}
\newunicodechar{π}{$\pi$}
\newunicodechar{∈}{$\in$}
\newunicodechar{⊞}{$\boxplus$}
\newunicodechar{⊠}{$\boxtimes$}
\newunicodechar{∁}{$\mathbb{C}$}
\newunicodechar{►}{$\blacktriangleright$}
\newunicodechar{▻}{$\vartriangleright$}
\newunicodechar{𝟙}{\textbf{1}}
\newunicodechar{∙}{$\cdot$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ℓ}{$\ell$}
\newunicodechar{∅}{$\varnothing$}
\newunicodechar{⟶}{$\rightarrow$}
\newunicodechar{□}{$\square$}
\newunicodechar{⇡}{$\uparrow$}
\newunicodechar{⊛}{$\circledast$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{⟨}{$\langle$}
\newunicodechar{⟩}{$\rangle$}
\newunicodechar{■}{$\blacksquare$}
\newunicodechar{∎}{$\blacksquare$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{⊕}{$\oplus$}
\newunicodechar{⊗}{$\otimes$}
\newunicodechar{∼}{$\sim$}
\newunicodechar{≈}{$\approx$}
\newunicodechar{⊔}{$\sqcup$}
\newunicodechar{⟦}{$\llbracket$}
\newunicodechar{⟧}{$\rrbracket$}
\newunicodechar{⊥}{$\bot$}
\newunicodechar{∞}{$\infty$}
\newunicodechar{⇑}{$\Uparrow$}
% Add more as you need them (shouldn't happen often).

@@

\newcommand{\GTT}{\textbf{GTT}}

@@

\section{Deep Embedding}
\label{sec:syntax}
\input{Prelude/Syntax}
\input{Streams}

@@

\subsection{Context Weakening and Clock Quantification}
\input{CloTT/TypeFormers/WeakenClock}
\input{CloTT/TypeFormers/ClockQuantification}

\subsection{The Later Modality}
\input{CloTT/TypeFormers/Later}
\input{CloTT/TypeFormers/Fix}
\input{CloTT/TypeFormers/Force}
